Baseline centering problem

### 2018-11-10 paper/advup_uniquesol.tex

>>>>

\paragraph{Removing $b$?} Let us just fix $b=0$ in the above. The unique
solution for $V$ (with $\gamma<1$) is
\begin{equation}
V(s)=V^\pi(s)+\left(\frac{1-\gamma}{\alpha}-1\right)\E_{\tilde \rho} V^\pi
\end{equation}
and with $\alpha=1$ this is simply
\begin{equation}
V(s)=V^\pi(s)-\gamma \E_{\tilde \rho} V^\pi
\end{equation}

Let us check the behavior of this when $\gamma\to 1$. We know that
\begin{equation}
V^\pi(s)=\frac{\E_{\rho^\pi}r}{1-\gamma}+U^\pi(s)+O(1-\gamma)
\end{equation}
with $\rho^\pi$ the invariant distribution from $\pi$, and $U$ the
relative value function of $\pi$. Thus, the fixed point for $V$ is
\begin{equation}
V(s)=U^\pi(s)-\gamma \E_{\tilde \rho}U^\pi +O(1-\gamma)
\end{equation}
which converges when $\gamma\to 1$???
